Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-11-10 paper/HH4b.tex
new section on PU

\abstract{
  The measurement of Higgs pair production is one of the cornerstones of
  the LHC program for the next years.
  %
  Double Higgs production provides a unique window to the electroweak
  symmetry breaking mechanism, and in particular it allows
  to access the Higgs trilinear coupling.
  %
  In this work we study the feasibility of the observation of the production of
  Higgs boson pairs at the High-Luminosity LHC (HL-LHC) in the
  $b\bar{b}b\bar{b}$ final state.
  %
  While the signal in this channel
  is enhanced by the large branching fraction of Higgs bosons to
  $b\bar{b}$ pairs, the measurement is  challenging due to the
  overwhelming QCD multijet background.
  %
  Our analysis is based on a combination of traditional cut-based
  methods with modern multivariate techniques, which lead to a substantial
  enhacement of the signal discrimination.
  %
  We account for  all relevant
  backgrounds, including the contribution from light jet fakes that is found
  to be as important or even dominant over the irreducible $4b$ QCD background.
  %
  By combining the contribution from the boosted, intermediate and resolved
  topologies we achieve a signal significance of $S/\sqrt{B}\simeq 3.2$.
  %
  We therefore demonstrate that at the HL-LHC the $b\bar{b}b\bar{b}$ channel alone
  should allow to claim evidence of the observation of double Higgs production.
}

@@

\input{sec-intro}
\input{sec-mcsamples}
\input{sec-analysis}
\input{sec-results}
\input{sec-mva}
\input{sec-optimisation}
\input{sec-conclusions}

>>>>

\abstract{
  The measurement of Higgs pair production is one of the cornerstones of
  the LHC program for the next years.
  %
  Double Higgs production provides a unique window to the electroweak
  symmetry breaking mechanism, and in particular it allows
  to access the Higgs trilinear coupling.
  %
  In this work we study the feasibility of the observation of the production of
  Higgs boson pairs at the High-Luminosity LHC (HL-LHC) in the
  $b\bar{b}b\bar{b}$ final state.
  %
  While the signal in this channel
  is enhanced by the large branching fraction of Higgs bosons to
  $b\bar{b}$ pairs, the measurement is  challenging due to the
  overwhelming QCD multijet background.
  %
  Our analysis is based on a combination of traditional cut-based
  methods with modern multivariate techniques, which lead to a substantial
  enhacement of the signal discrimination.
  %
  We account for  all relevant
  backgrounds, including the contribution from light jet fakes that is found
  to be as important or even dominant over the irreducible $4b$ QCD background.
  %
  By combining the contribution from the boosted, intermediate and resolved
  topologies we achieve a signal significance of $S/\sqrt{B}\simeq 3.2$.
  %
  We demonstrate the robustness of our analysis under realistic
  pile-up conditions expected at the HL-LHC
  %
  We therefore conclude
  that at the HL-LHC the $b\bar{b}b\bar{b}$ channel alone
  should allow to claim evidence of the observation of double Higgs production.
}

@@

\input{sec-intro}
\input{sec-mcsamples}
\input{sec-analysis}
\input{sec-results}
\input{sec-mva}
\input{sec-pileup}
\input{sec-conclusions}
